Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-16 paper.qmd
Updated error plot

error_plot_scurve <- error_df_scurve |>
  ggplot(aes(x = UMAP1,
             y = UMAP2,
             color = type)) +
  geom_point(alpha=0.5) +
  theme(
    legend.position = "bottom"
  )
```

```{r}
#| label: fig-p-d-error-in-2d-scurve
error_plot_scurve
```

>>>>

error_plot_scurve <- error_df_scurve |>
  ggplot(aes(x = UMAP1,
             y = UMAP2,
             color = type)) +
  geom_point(alpha=0.5) +
  scale_colour_brewer(
    type = "qual",
    palette = 2
  ) +
  theme(
    legend.position = "right",
    legend.text = element_text(size = 10)
  ) +
  coord_equal()
```

```{r}
#| label: fig-p-d-error-in-2d-scurve
#| fig-cap: "error"
#| out-height: 30%
#| fig-pos: H

error_plot_scurve
```
